1_bigsnpr_gwas_prep

### 2020-01-07 analysis/1_bigsnpr_gwas_prep.Rmd
Mash analysis of GR50 and FL50 with plots

@@

```{r}
markers2sub <- attr(svd, "subset")
markers2 <- tibble(CHR = CHR[markers2sub], POS = POS[markers2sub])

gwas_rds <- pvdiv_results_in_folder(path = ".", pattern = "GWAS_object_") # 8 phenotypes from 4 sites - 32 phenotypes total with > 200 individuals phenotyped and sequenced.

>>>>

# T_GR_FL

phe_gwas_tgrfl <- phenotypes_wide_2019 %>%
  dplyr::select(-colremove) %>%
  dplyr::select(PLANT_ID, ends_with("T_GR_FL"))

  plants <- plants %>% enframe(value="PLANT_ID") %>% dplyr::select(-name)
  plants %>%
    left_join(phe_gwas_tgrfl) %>% arrange(PLANT_ID)

  df_phe <- plants %>%
    left_join(phe_gwas_tgrfl)

# Mash 8 sites T_GR_FL
```{r}
load(file = "../markers.rda")
load(file = "../markers_unlinked.rda")
gwas_rds <- pvdiv_results_in_folder(path = ".", pattern = "GWAS_object_") # 8 phenotypes from 4 sites - 32 phenotypes total with > 200 individuals phenotyped and sequenced.

numSNPs <- ceiling(1000000/length(phenotype_names)^2)
numSNPs <- 20000 # the above gave 20409, so just rounded this to 20000.

mash_output <- mash_standard_run(path = ".", list_input = mash_input, 
                                  numSNPs = numSNPs, saveoutput = TRUE)

anno_tables <- pvdiv_table_topsnps(df = mash_output, type = "mash", 
                                   n = c(10,100), FDRalpha = NA, 
                                   rangevector = c(0, 20000, 100000),
                                   markers = markers, 
                                   anno_info = gene_anno_info,
                                   txdb = txdb)
saveRDS(anno_tables, file.path("~", "Github", "pvdiv-phenology-gxe", 
                               "large-files", "T_GR_FL", 
                               paste0("Annotation_tables_", 
                                      "Time_greenup_to_flowering_date_mash_", 
                                      "7_sites_9_PCs.rds")))
nbycond <- mash_plot_sig_by_condition(m = mash_output, saveoutput = TRUE)
mashhattan <- mash_plot_manhattan_by_condition(m = mash_output, saveoutput = TRUE)

mhtn <- mashhattan$ggmanobject + scale_color_viridis(option = "B",  end = 0.8) + scale_fill_viridis(option = "B", end = 0.8)

save_plot("Manhattan_T_GR_FL.png", plot = last_plot(), base_height = 4, base_asp = 2.5)

pairwise_plot <- mash_plot_pairwise_sharing(effectRDS = "Pairwise_sharing_Strong_Effects_26989SNPs.rds", reorder = TRUE, saveoutput = TRUE)
save_plot("Pairwise_test.png", plot = pairwise_plot$gg_corr, base_height = 2.5, base_asp = 1.618)
```

# FL50

phe_gwas_fl50 <- phenotypes_wide_2019 %>%
  dplyr::select(-colremove) %>%
  dplyr::select(PLANT_ID, ends_with("FL50"))

  plants <- plants %>% enframe(value="PLANT_ID") %>% dplyr::select(-name)
  plants %>%
    left_join(phe_gwas_fl50) %>% arrange(PLANT_ID)

  df_phe <- plants %>%
    left_join(phe_gwas_fl50)

# Mash FL50
```{r}
load(file = "../markers.rda")
load(file = "../markers_unlinked.rda")
gwas_rds <- pvdiv_results_in_folder(path = ".", pattern = "GWAS_object_") # 8 phenotypes from 4 sites - 32 phenotypes total with > 200 individuals phenotyped and sequenced.

numSNPs <- ceiling(1000000/length(phenotype_names)^2)
numSNPs <- 20000 # the above gave 20409, so just rounded this to 20000.

mash_output <- mash_standard_run(path = ".", list_input = mash_input, 
                                  numSNPs = numSNPs, saveoutput = TRUE)

anno_tables <- pvdiv_table_topsnps(df = mash_output, type = "mash", 
                                   n = c(10,100), FDRalpha = NA, 
                                   rangevector = c(0, 20000, 100000),
                                   markers = markers, 
                                   anno_info = gene_anno_info,
                                   txdb = txdb)
saveRDS(anno_tables, file.path("~", "Github", "pvdiv-phenology-gxe", 
                               "large-files", "T_GR_FL", 
                               paste0("Annotation_tables_", 
                                      "Flowering_date_mash_", 
                                      "7_sites_9_PCs.rds")))
```

```{r}
anno_tables <- readRDS("../PAG/FL50/Annotation_tables_Flowering_date_mash_7_sites_9_PCs.rds")
mash_output <- readRDS(file = "../PAG/FL50/Strong_Effects29475SNPs.rds")
anno_tables$top100SNPs_within0bp %>%
  arrange(desc(log10BayesFactor))

nbycond <- mash_plot_sig_by_condition(m = mash_output, saveoutput = TRUE)
mashhattan <- mash_plot_manhattan_by_condition(m = mash_output)

mhtn <- mashhattan$ggmanobject + scale_color_viridis(option = "B",  end = 0.8) + scale_fill_viridis(option = "B", end = 0.8)

save_plot("Manhattan_FL50.png", plot = last_plot(), base_height = 4, base_asp = 2.5)

pairwise_plot <- mash_plot_pairwise_sharing(effectRDS = "../PAG/FL50/Pairwise_sharing_Strong_Effects_29475SNPs.rds", reorder = FALSE)
save_plot("Pairwise_FL50_unordered.svg", plot = pairwise_plot$gg_corr, base_height = 2.5, base_asp = 1.618)

pairwise_plot2 <- mash_plot_pairwise_sharing(effectRDS = "../PAG/T_GR_FL/Pairwise_sharing_Strong_Effects_26989SNPs.rds", reorder = FALSE)
save_plot("Pairwise_T_GR_FL_unordered.svg", plot = pairwise_plot2$gg_corr, base_height = 2.5, base_asp = 1.618)

pairwise_plot3 <- mash_plot_pairwise_sharing(effectRDS = "../PAG/GR50/Pairwise_sharing_Strong_Effects_31355SNPs.rds", reorder = FALSE)
save_plot("Pairwise_GR50_unordered.svg", plot = pairwise_plot3$gg_corr, base_height = 2.5, base_asp = 1.618)

library(ggcorrplot)
ggcorrplot(pairwise_plot$corr_matrix[c(4,6,8,7,2,5,3,1),c(4,6,8,7,2,5,3,1)])
save_plot("Pairwise_FL50_latitude.svg", plot = last_plot(), base_height = 2.5, base_asp = 1.618)

ggcorrplot(pairwise_plot2$corr_matrix[c(5,7,6,2,4,3,1),c(5,7,6,2,4,3,1)])
save_plot("Pairwise_T_GR_FL_latitude.svg", plot = last_plot(), base_height = 2.5, base_asp = 1.618)

ggcorrplot(pairwise_plot3$corr_matrix[c(5,8,10,7,9,2,6,3,4,1),c(5,8,10,7,9,2,6,3,4,1)])
save_plot("Pairwise_GR50_latitude.svg", plot = last_plot(), base_height = 2.5, base_asp = 1.618)

@@

```{r}
svd <- readRDS(file.path("/", "home", "alice", "Github", "pvdiv-phenology-gxe",
                         "large-files", "SVD_upland_lowland_continuous_k20.rds"))

  G <- snp$genotypes
  CHR <- snp$map$chromosome
  POS <- snp$map$physical.pos
  plants <- snp$fam$sample.ID

markers <- tibble(CHR = CHR, POS = POS)

markers2sub <- attr(svd, "subset")
markers2 <- tibble(CHR = CHR[markers2sub], POS = POS[markers2sub])

save(markers, file = "markers.rda")
save(markers2, file = "markers_unlinked.rda")

```{r}
load(file = "markers.rda")
load(file = "markers_unlinked.rda")
gwas_rds <- pvdiv_results_in_folder(path = ".", pattern = "GWAS_object_") # 8 phenotypes from 4 sites - 32 phenotypes total with > 200 individuals phenotyped and sequenced.
